---
title: "Example Starter R Script"
output: html_document
---

## Introduction and background
This is meant to be a sample starter script if you choose to use R for this case study. This is not comprehensive of everything you'll do in the case study, but should be used as a starting point if it is helpful for you.

```{r}
install.packages('tidyverse')
library(tidyverse)
setwd("C:\\Users\\Kevin\\Desktop\\homework\\CaseStudy1")
```


## Loading your CSV files
Here we'll create a dataframe named 'stations' and read in one of the CSV files from the dataset.

```{r}
stations <- read.csv("Divvy_Stations_2014-Q1Q2.csv")
```

We'll create another dataframe for the trips data. 
```{r}
trips <- read.csv("Divvy_Trips_2014_Q1Q2.csv")
```

## Exploring a few key tables

Take a look at the stations data.
```{r}
head(stations)
```

Identify all the columsn in the stations data.
```{r}
colnames(stations)
```

Take a look at the trips data.
```{r}
head(trips)
```

Identify all the columsn in the trips data.
```{r}
colnames(trips)
```

Note that both datasets have the 'Id' field - this can be used to merge the datasets.

## Understanding some summary statistics
How many unique participants are there in each dataframe? It looks like there may be more participants in the stations dataset than the trips dataset.

```{r distinct users}
n_distinct(stations$id)
n_distinct(trips$trip_id)
```

How many observations are there in each dataframe?
```{r observations}
nrow(stations)
nrow(trips)
```
Merge data to 1 data frame by using start point and stations name
```{r}
stations_trips <- merge(stations, trips, by.x=c("id"), by.y=c("from_station_id"))
```



What are some quick summary statistics we'd want to know about each data frame?

For the stations dataframe:
```{r}
stations_trips %>%  
  select(dpcapacity,
         tripduration) %>%
  summary()
```

Calculate the group of male and female of subscriber of lending bikes
```{r}
user_summanry <- stations_trips %>%  
  count(usertype, gender, sort=TRUE)
```